Racial and Ethnic Differences in ETI: Outcomes

### 2024-07-07 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti_outcomes.qmd
double check hospitalization code!

```{r data import}
# source("/home/timvigers/GitHub/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/create_outcomes_dataset.R")
load("./Kamyron Jordan/Racial and Ethnic Differences in ETI/Data_Cleaned/outcomes_dataset.RData")
```

>>>>

```{r data import and minor cleaning}
# Run code for base dataset (takes forever)
# source("/home/timvigers/GitHub/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/create_outcomes_dataset.R")
# Import
load("./Kamyron Jordan/Racial and Ethnic Differences in ETI/Data_Cleaned/outcomes_dataset.RData")
# Additional quick cleaning steps
# Remove impossible lung function values
encounter$gli_fev1_ppred_rn[encounter$gli_fev1_ppred_rn < 20 |
  encounter$gli_fev1_ppred_rn > 150] <- NA
encounter$gli_fvc_ppred_rn[encounter$gli_fvc_ppred_rn < 20 |
  encounter$gli_fvc_ppred_rn > 150] <- NA
encounter$gli_fev1fvc_ppred_rn[encounter$gli_fev1fvc_ppred_rn < 20 |
  encounter$gli_fev1fvc_ppred_rn > 150] <- NA
# Filter
encounter <- encounter %>%
  filter(
    !is.na(Days),
    Days >= -365.25 * 3 & Days <= 365.25 * 2,
    hospitalized == "No",
    pregnant != 1
  )
```
